A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-11 sanity/paper1.tex
\url for links
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1054 43ef1190-90fd-4dd7-a769-d0121f02b80e

We find that only one SPARQL endpoint yields a heuristic lifetime, on
closer inspection, we find this to be hosted by
Dydra\footnote{http://dydra.com/}. We speculate that this is due to
that few underlying DBMS systems help track modification times in a
way that can be used on a SPARQL result basis.

>>>>

We find that only one SPARQL endpoint yields a heuristic lifetime, on
closer inspection, we find this to be hosted by
Dydra\footnote{\url{http://dydra.com/}}. We speculate that this is due to
that few underlying DBMS systems help track modification times in a
way that can be used on a SPARQL result basis.
